A Method for Analysing Heterogeneous Data with 2D Detection Function Distance Sampling

### 2018-04-23 Draft.tex
4/23 #2

Given that the LT2D source code is approximately 3500 lines of R code after the completion of this project, and that the inclusions which constitute this project are over 1500 alone, GitHub links to the relevant files will be included to avoid bloating this document.

@@

>>>>

Given that the LT2D source code is approximately 3500 lines of R code (after the completion of this project), and that the inclusions which constitute this project are over 1500 alone, GitHub links to the relevant files will be included to avoid bloating this document.

@@

\url{https://github.com/penguin-coding/LT2D-work/blob/master/LatexRCode.R}
